GSEA datasets for FDR benchmarking

### 2017-10-30 datasets/GSEA/gsea.Rmd
Added new buildBench ftCols code to GSEA

```{r informativeCovariate, message=FALSE, fig.height=3.5, message=FALSE, fig.width=4.5}
library(ggplot2)
library(magrittr)
library(cowplot)
library(R.utils)
library(scales)
sourceDirectory("../R/")

@@

```{r runningBenckmark, message=FALSE}
designBen <- initializeBenchDesign()
res <- dplyr:::select( goRes, c("over_represented_pvalue", "numInCat") ) %>%
  dplyr:::rename( pval = over_represented_pvalue, ind_covariate = numInCat )
res$pval <- pmin( res$pval, 1 )
sGSEA <- designBen %>% buildBench( res )
assayNames(sGSEA) <- "qvalue"
sGSEA <- addDefaultMetrics( sGSEA )
```

@@

stopifnot( all(assays(sGSEA)[["qvalue"]][,"unadjusted"] == pmin(goRes$over_represented_pvalue, 1) ) )
rowData(sGSEA)$numInCat <- goRes$numInCat

rejection_scatter_bins( sGSEA, "numInCat", threshold=15, bins=4, as_fraction=TRUE )
```

>>>>

```{r informativeCovariate, message=FALSE, fig.height=3.5, message=FALSE, fig.width=4.5}

library(ggplot2)
library(magrittr)
library(cowplot)
library(R.utils)
library(scales)
sourceDirectory("../R/")

@@

```{r runningBenckmark, message=FALSE}
designBen <- initializeBenchDesign()
res <- dplyr:::select( goRes, c("over_represented_pvalue", "numInCat") ) %>%
  dplyr:::rename( pval = over_represented_pvalue, ind_covariate = numInCat )
res$pval <- pmin( res$pval, 1 )
head(res)
sGSEA <- designBen %>% buildBench( res, ftCols="ind_covariate")
elementMetadata( rowData(sGSEA) )
assayNames(sGSEA) <- "qvalue"
sGSEA <- addDefaultMetrics( sGSEA )
```

@@

stopifnot( all(assays(sGSEA)[["qvalue"]][,"unadjusted"] == pmin(goRes$over_represented_pvalue, 1) ) )

sGSEA <- estimatePerformanceMetrics(sGSEA, addColData=TRUE)
rejection_scatter_bins( sGSEA, "ind_covariate", threshold=15, bins=4, as_fraction=TRUE )
